#Analysis

##Task

All tasks lies below:

1. a tidy data set
2. a link to Github with the analysis script
3. a coodbook which describes work

In this script, I'll finish these things:

1. Merge the traing and test sets to create one data set
2. Extracts only the measurements on the mean and sandard deviation for each measurement
3. Uses descriptive activity names to name the activities in the data set
4. Appropriately labels the data set with descriptive activity names
5. Creates a second, independent tidy data set with the average of each variable for each activity and each subject

##Preliminaries
First, donlowd the file and unzip it manually, then set path 
```{r}
setwd('/Users/yangguangyao/Documents/GitHub_Project/GettingCleaningDataProject/UCI HAR Dataset')
getwd()
```


##Read files
```{r}
subject_train = read.table('./train/subject_train.txt')
X_train = read.table('./train/X_train.txt')
y_train = read.table('./train/y_train.txt')
subject_test = read.table('./test/subject_test.txt')
X_test = read.table('./test/X_test.txt')
y_test = read.table('./test/y_test.txt')
```

##Merge data
Merge the traing、test and subject dataset and we get tidy data where train and test data are included
```{r}
X = rbind(X_train,X_test)
Y = rbind(y_train,y_test)
subject = rbind(subject_train,subject_test)
data = cbind(X,Y,subject)
dim(data)
```

##Extract mean and sd value
```{r}
col_mean = colMeans(data)
col_sd = sapply(data,sd)
list(col_mean = col_mean, col_sd = col_sd)
```

##Use descriptive activity names
```{r}
activity_label  = read.table('activity_labels.txt')
names(data)[c(562,563)] = c('V562','V563')
#merge process，add descriptive names to data and we get data1
data1 = merge(data,activity_label,by.x = "V562",by.y = "V1")
names(data1)
```

##Label data and get data2
In data2, the first 561 attribute represents x, the 562th represents subject, the 563th and 564 represent y value.
```{r}
features = as.character(read.table('features.txt')$V2) # length 561
features = c('y_code',features,'subject','y_desc')
names(data1) = features
#names(data1)
data2 = data1[,c(2:562,563,1,564)]
names(data2)
```

##Second tidy data set and we get list_group_split
```{r}
data_split = split(data2,data2$y_desc)
list_group_splist = sapply(data_split,function(x) {
colMeans(x[,1:562])
})
list_group_splist
```

##Write data
```{r}
write.table(data2,file = 'data.txt')
```